\medskip

\begin{thebibliography}{1}

\bibitem{Christensen_twitterRevolutions} Christensen, C. (2011). Twitter revolutions? Addressing social media and dissent. The Communication Review, 14(3), 155-157.

\bibitem{deArruda_socialContaigonHypergraphs} de Arruda, G. F., Petri, G., \& Moreno, Y. (2019). Social contagion models on hypergraphs. arXiv preprint arXiv:1909.11154.

\bibitem{Ferrara_frenchElection} Ferrara, E. (2017). Disinformation and social bot operations in the run up to the 2017 French presidential election. First Monday, 22(8).

\bibitem{Goncalves_dunbarsNumber} Gonçalves, B., Perra, N., \& Vespignani, A. (2011). Modeling users' activity on twitter networks: Validation of dunbar's number. PloS one, 6(8).

\bibitem{Gorwa_typologyGuideToSocialBots} Gorwa, R., \& Guilbeault, D. (2018). Unpacking the social media bot: A typology to guide research and policy. Policy \& Internet.

\bibitem{Howard_botsBrexit} Howard, P. N., \& Kollanyi, B. (2016). Bots,\# StrongerIn, and\# Brexit: computational propaganda during the UK-EU referendum. Available at SSRN 2798311.

\bibitem{Iacopini_simplicialContaigon} Iacopini, I., Petri, G., Barrat, A., \& Latora, V. (2019). Simplicial models of social contagion. Nature communications, 10(1), 2485.

\bibitem{Luceri_evolutionOfTwitterBots} Luceri, L., Deb, A., Giordano, S., \& Ferrara, E. (2019). Evolution of bot and human behavior during elections. First Monday, 24(9).

\bibitem{Mittal_automatedHighImpact} Mittal, S., \& Kumaraguru, P. (2014). Broker Bots: Analyzing Automated Activity During High Impact Events on Twitter. arXiv preprint arXiv:1406.4286.

\bibitem{Murthy_twitterMasses} Murthy, D. (2011). Twitter: Microphone for the masses?. Media, culture \& society, 33(5), 779-789.

\bibitem{Neudert_botsGermany} Neudert, L., Kollanyi, B., \& Howard, P. N. (2017). Junk news and bots during the german parliamentary election: What are german voters sharing over twitter?.

\bibitem{Newman_AssortMixing} Newman, M. E. (2002). Assortative mixing in networks. Physical review letters, 89(20), 208701.

\bibitem{Shao_spreadOfFakeNews} Shao, C., Ciampaglia, G. L., Varol, O., Flammini, A., \& Menczer, F. (2017). The spread of fake news by social bots. arXiv preprint arXiv:1707.07592, 96-104.

\bibitem{Smith_polarizedCrowds} Smith, M. A., Rainie, L., Shneiderman, B., \& Himelboim, I. (2014). Mapping Twitter topic networks: From polarized crowds to community clusters. Pew Research Center, 20, 1-56.

\bibitem{Subrahmanian_DARPAbotChallenge} Subrahmanian, V. S., Azaria, A., Durst, S., Kagan, V., Galstyan, A., Lerman, K., ... \& Menczer, F. (2016). The DARPA Twitter bot challenge. Computer, 49(6), 38-46.

\end{thebibliography}